---
title: "Misc"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Adding metadata

One nice feature of quanteda is that we can easily add metadata to the corpus object.

```{r}
docvars(twcorpus) <- data.frame(screen_name=tweets$screen_name, polite=tweets$polite)
summary(twcorpus)
```

We can then use this metadata to subset the dataset:

```{r}
polite.tweets <- corpus_subset(twcorpus, polite=="impolite")
```

And then extract the text:
```{r}
mytexts <- texts(polite.tweets)
```

We'll come back later to this dataset.



### Importing text with quanteda

There are different ways to read text into `R` and create a `corpus` object with `quanteda`. We have already seen the most common way, importing the text from a csv file and then adding the metadata, but `quanteda` has a built-in function to help with this:

```{r}
library(readtext)
tweets <- readtext(file='data/EP-elections-tweets.csv')
twcorpus <- corpus(tweets)
```

This function will also work with text in multiple files. To do this, we use the textfile command, and use the 'glob' operator '*' to indicate that we want to load multiple files:

```{r}
myCorpus <- readtext(file='data/inaugural/*.txt')
inaugCorpus <- corpus(myCorpus)
```

