---
title: "(Advanced) topic models"
author: Pablo Barbera
date: July 4, 2018
output: html_document
---

## Topic Modeling: Structural Topic Model

```{r message = FALSE}
library(topicmodels)
# reading data and preparing corpus object
nyt <- read.csv("../data/nytimes.csv", stringsAsFactors = FALSE)
library(quanteda)
nytcorpus <- corpus(nyt$lead_paragraph)
nytdfm <- dfm(nytcorpus, remove=stopwords("english"), verbose=TRUE,
               remove_punct=TRUE, remove_numbers=TRUE)
cdfm <- dfm_trim(nytdfm, min_docfreq = 2)

```

Most text corpora have not only the documents per se, but also a lot of metadata associated -- we know the author, characteristics of the author, when the document was produced, etc. The structural topic model takes advantage of this metadata to improve the discovery of topics. Here we will learn how it works, how we can interpret the output, and some issues related to its usage for research.

We will continue with the previous example, but now adding one covariate: the party of the president.

```{r}
library(stm)
# extracting covariates
year <- as.numeric(substr(nyt$datetime, 1, 4))
repub <- ifelse(year %in% c(1981:1992, 2000:2008), 1, 0)
```

And now we're ready to run `stm`!

```{r, eval=FALSE}
# metadata into a data frame
meta <- data.frame(year=year, repub=repub)
# running STM
stm <- stm(documents=cdfm, K=30, prevalence=~repub+s(year),
           data=meta, seed=123)
save(stm, file="../backup/stm-output.Rdata")
```

`stm` offers a series of features to explore the output. First, just like LDA, we can look at the words that are most associated with each topic.

```{r}
load("../backup/stm-output.Rdata")
# looking at a few topics
labelTopics(stm, topics=1)
labelTopics(stm, topics=4)
labelTopics(stm, topics=7)
labelTopics(stm, topics=10)
```

But unlike LDA, we now can estimate the effects of the features we considered into the prevalence of different topics

```{r}
# effects
est <- estimateEffect(~repub, stm,
	uncertainty="None")
labelTopics(stm, topics=1)
summary(est, topics=1)

labelTopics(stm, topics=4)
summary(est, topics=4)

labelTopics(stm, topics=7)
summary(est, topics=7)

labelTopics(stm, topics=9)
summary(est, topics=9)
```

Let's say we're interested in finding the most partisan topics. How would we do this?

```{r}
# let's look at the structure of the output object...
names(est)
length(est$parameters)
est$parameters[[1]]

# aha! we'll just extract the coefficients for each topic
coef <- se <- rep(NA, 30)
for (i in 1:30){
	coef[i] <- est$parameters[[i]][[1]]$est[2]
	se[i] <- sqrt(est$parameters[[i]][[1]]$vcov[2,2])
}

df <- data.frame(topic = 1:30, coef=coef, se=se)
df <- df[order(df$coef),] # sorting by "partisanship"
head(df[order(df$coef),])
tail(df[order(df$coef),])

# three most "democratic" topics
labelTopics(stm, topics=df$topic[1])
labelTopics(stm, topics=df$topic[5])
labelTopics(stm, topics=df$topic[26])

# three most "republican" topics
labelTopics(stm, topics=df$topic[16])
labelTopics(stm, topics=df$topic[28])
labelTopics(stm, topics=df$topic[11])
```

